\textsc{Beyond the Iceberg Hypothesis: \\Opening the Black Box of Transport Costs}

### 2017-09-13 redaction/dhp_july2017.tex
Nouvelle version du papier et de l'annexe online

Our first contribution to the literature is to provide estimates for the size of both the ad-valorem and the additive components of transport costs. Table \ref{tab:summary_results} reports a summary of our results. It displays the mean and median values of each type of trade costs (either ad-valorem estimated alone or estimated along with additive costs), as well as the associated standard deviation, averaged over the period 1974-2013, for estimation driven both at the 3- and 4-digit sectorial level for different specifications and data. The first panel reports the results for a specification based on ad-valorem costs estimated alone (Equation (\ref{eq:model_nlI})), while the second panel presents estimates for a specification involving both ad-valorem and multiplicative components (Equation (\ref{eq:model_IetA})). Finally, the third panel reports the same set of descriptive statistics, but for the actual cif/fas ratio in our data.\footnote{In Appendix \ref{app:more_results}, we report similar results for a sample of years, for both transport mode, at the 3 and 4-digit classification level. Results for all years (available at the 3-digit level) are available upon request to the authors.}$^{,}$\footnote{We present the estimation results for Air at the 3-digit level removing the year 1989, as the results reveal the presence of strong outliers that bias the estimates of transport costs upwards this particular year. Overall results (over the whole period) are not substantially affected if this year is included though. These results are available upon request to the authors.}

@@

\noindent where $\mathbb{1}_i$ and $\mathbb{1}_{s(k)}$ represent country- and sector- fixed effects.\footnote{Throughout the exercice, we consider Argentina, the sector 011 and the first year of our dataset 1974, as references for the country-, product and -year dummies.}  Equation (\ref{eq:compeffects_mult}) is estimated using OLS, with a weighting scheme based on the value of each flow in the total value of flows the considered year. As for the additive component, given that the sector fixed effect and the country fixed effect are additive rather than multiplicative by construction, ee estimate the following equation using non-linear least squares:\footnote{For sake of notational simplicity, we do not distinguish the coefficients associated to the fixed effects between Equations (\ref{eq:compeffects_mult}) and (\ref{eq:compeffects_add}), even if they are specific to the type of transport costs considered (e.g., the series of $\gamma_t$ differs from one estimation to the other). Note that we impose the same weighting scheme as for the OLS regression (based on the relative value of the flow).}
%, based on the additive cost series $\widehat{t}_{ikt}$ previously obtained:
\begin{eqnarray}
\ln(\widehat{t}_{ikt})&=&\ln\left( \delta + \underbrace{\sum_{i \neq \text{ARG}}  \alpha_i.\mathbb{1}_i}_{(a)}+\underbrace{\sum_{s(k)}\beta_{s(k)}.\mathbb{1}_{s(k)}}_{(b)}\right) + \underbrace{\sum_{t \neq 1974}\gamma_t.\mathbb{1}_t}_{(c)}+\epsilon_{ikt} \label{eq:compeffects_add}
\end{eqnarray}
As displayed in Equations (\ref{eq:compeffects_mult}) and (\ref{eq:compeffects_add}), the objective is to decompose the estimated transport cost component in three components: The country dimension (Term (a)), the product dimension (Term (b)) and the ``ceteris paribus'' transport costs time trend (Term (c)). Notice that Equations (\ref{eq:compeffects_mult}) and (\ref{eq:compeffects_add}) preserve our specification of the ad-valorem and additive costs of Equations (\ref{eq:ad-valorem}) and (\ref{eq:add}), as we consider that the iceberg cost is the product of the country of origin and the good dimension, while the additive cost is the sum of the two dimensions. Both equations are estimated by transport mode.

@@

Third, in contrast to us, \cite{hummels2007} does not purge its measure of the fitted ad-valorem rate by the country-sector fixed effects. This is not likely to make a substantial difference though, as these fixed effects are by nature constant over time. Accordingly, they only play as a scale effect as the estimate is in log. Fourth, we differ in the weighting scheme retained to obtain the yearly value of the fitted transport cost (in the terms of \citeh{hummels2007} method, the switch from $\widehat{TC}_{ikt}$ to $\widehat{TC}_{t}$, Equations (\ref{eq:comp_effects_adv}) and (\ref{eq:comp_effects_add}) in our case). \cite{hummels2007} takes the unweighed average value over the $i,k$ dimension, which implicitly attributes a weight equal to 1 to each flow. We proceed differently, as we weight each flow by its relative value on total trade flows observed in 1974. This choice is made for two reasons. First, this weighting scheme does not overweight the small flows in value. Second, considering the 1974 weighting scheme makes sense as starting point of our time trend analysis. However, we ensure that our results are not sensitive to an alternative weighting scheme, by building the average fitted transport costs rate as in \cite{hummels2007} (Results available upon request to the authors).

%\textbf{These results are reported in ???}.

>>>>

Our first contribution to the literature is to provide estimates for the size of both the ad-valorem and the additive components of transport costs. Table \ref{tab:summary_results} reports a summary of our results. It displays the mean and median values of each type of trade costs (either ad-valorem estimated alone or estimated along with additive costs), as well as the associated standard deviation, averaged over the period 1974-2013, for estimation driven both at the 3- and 4-digit sectorial level for different specifications and data. The first panel reports the results for a specification based on ad-valorem costs estimated alone (Equation (\ref{eq:model_nlI})), while the second panel presents estimates for a specification involving both ad-valorem and multiplicative components (Equation (\ref{eq:model_IetA})). Finally, the third panel reports the same set of descriptive statistics, but for the actual cif/fas ratio in our data.\footnote{In Appendix \ref{app:more_results}, we report similar results for a sample of years, for both transport mode, at the 3 and 4-digit classification level. Results for all years (available at the 3-digit level) are reported in the Online Appendix, available on the authors' webpages.}$^{,}$\footnote{We present the estimation results for Air at the 3-digit level removing the year 1989, as the results reveal the presence of strong outliers that bias the estimates of transport costs upwards this particular year. Overall results (over the whole period) are not substantially affected if this year is included though. This can be uncovered from the results detailed year by year in the Online Appendix, available on the authors' webpages.}

@@

\noindent where $\mathbb{1}_i$ and $\mathbb{1}_{s(k)}$ represent country- and sector- fixed effects.\footnote{Throughout the exercise, we consider Argentina, the sector 011 and the first year of our dataset 1974, as references for the country-, product and -year dummies.}  Equation (\ref{eq:compeffects_mult}) is estimated using OLS, with a weighting scheme based on the value of each flow in the total value of flows the considered year. As for the additive component, given that the sector fixed effect and the country fixed effect are additive rather than multiplicative by construction, ee estimate the following equation using non-linear least squares:\footnote{For sake of notational simplicity, we do not distinguish the coefficients associated to the fixed effects between Equations (\ref{eq:compeffects_mult}) and (\ref{eq:compeffects_add}), even if they are specific to the type of transport costs considered (e.g., the series of $\gamma_t$ differs from one estimation to the other). Note that we impose the same weighting scheme as for the OLS regression (based on the relative value of the flow).}
%, based on the additive cost series $\widehat{t}_{ikt}$ previously obtained:
\begin{eqnarray}
\ln(\widehat{t}_{ikt})&=&\ln\left( \delta + \underbrace{\sum_{i \neq \text{ARG}}  \alpha_i.\mathbb{1}_i}_{(a)}+\underbrace{\sum_{s(k)}\beta_{s(k)}.\mathbb{1}_{s(k)}}_{(b)}\right) + \underbrace{\sum_{t \neq 1974}\gamma_t.\mathbb{1}_t}_{(c)}+\epsilon_{ikt} \label{eq:compeffects_add}
\end{eqnarray}
As displayed in Equations (\ref{eq:compeffects_mult}) and (\ref{eq:compeffects_add}), the objective is to decompose the estimated transport cost component in three components: The country dimension (Term (a)), the product dimension (Term (b)) and the ``ceteris paribus'' transport costs time trend (Term (c)). Notice that Equations (\ref{eq:compeffects_mult}) and (\ref{eq:compeffects_add}) preserve our specification of the ad-valorem and additive costs of Equations (\ref{eq:ad-valorem}) and (\ref{eq:add}), as we consider that the iceberg cost is the product of the country of origin and the good dimension, while the additive cost is the sum of the two dimensions. Both equations are estimated by transport mode.

@@

Third, in contrast to us, \cite{hummels2007} does not purge its measure of the fitted ad-valorem rate by the country-sector fixed effects. This is not likely to make a substantial difference though, as these fixed effects are by nature constant over time. Accordingly, they only play as a scale effect as the estimate is in log. Fourth, we differ in the weighting scheme retained to obtain the yearly value of the fitted transport cost (in the terms of \citeh{hummels2007} method, the switch from $\widehat{TC}_{ikt}$ to $\widehat{TC}_{t}$, Equations (\ref{eq:comp_effects_adv}) and (\ref{eq:comp_effects_add}) in our case). \cite{hummels2007} takes the unweighed average value over the $i,k$ dimension, which implicitly attributes a weight equal to 1 to each flow. We proceed differently, as we weight each flow by its relative value on total trade flows observed in 1974. This choice is made for two reasons. First, this weighting scheme does not overweight the small flows in value. Second, considering the 1974 weighting scheme makes sense as starting point of our time trend analysis. However, we ensure that our results are not sensitive to an alternative weighting scheme, by building the average fitted transport costs rate as in \cite{hummels2007}, as reported in Section \ref{sec:robustness}.
